Computation and comparison of the stable northeastern United States marine boundary layer

### 2020-12-09 Paper/methodology.tex

\subsubsection{Determination of surface roughness and prescribed temperature }
To match the measured TI conditions given in Table
\ref{tab:CapeWindMeasurements}, the surface roughness and prescribed
surface temperature change were adjusted through an initial
trial-and-error process.  The final surface roughness of $z_0$=0.0005 m
used for the stable offshore conditions (see Table~\ref{tab:z0tempparam})
matched the roughness used in the neutral 15 m/s and unstable 5 m/s and
10 m/s cases from the previous study \cite{cheung2020large}.  This
value of surface roughness is consistent with the measurements from
the North Sea \cite{taylor2001dependence}, which found values of $z_0$
ranging from $5 \times 10^{-5}$m to $5\times 10^{-3}$ m.

>>>>

\subsubsection{Determination of surface roughness and prescribed temperature }
To match the measured TI conditions given in Table
\ref{tab:CapeWindMeasurements}, the surface roughness and prescribed
surface temperature change were adjusted through an initial
trial-and-error process.  The final surface roughness of $z_0$=0.0005 m
used for the stable offshore conditions (see Table~\ref{tab:z0tempparam})
matched the roughness used in the neutral 15 m/s and unstable 5 m/s and
10 m/s cases from the previous study \cite{cheung2020large}.  This
value of surface roughness is consistent with the measurements from
the North Sea \cite{taylor2001dependence}, which found values of $z_0$
ranging from $5 \times 10^{-5}$ m to $5\times 10^{-3}$ m.

### 2020-12-09 Paper/results.tex

\subsection{\label{sec:gridstudy}Domain and grid resolution study}

@@

>>>>

\subsection{\label{sec:gridstudy}Domain and mesh resolution study}

@@

Note that in this paper, we focus our attention on the horizontal
resolution required to resolve key physical features in the SBL, and
some additional impacts deserve additional study.  For instance, the
impact of non-isotropic meshes with the k-sgs turbulence model and
wall function treatment is not addressed here and worthy of additional
attention.
